### 2018-02-05 Cars/paper.tex
lane changes

\begin{center}
\begin{table}[h]
\resizebox{\textwidth}{!}{%
\begin{tabular}{| l | c | c | c |}
\hline
& Non-Informative Prior & Simple Hierarchy & Finite Mixture Hierarchy \\
\hline
MCMC & \multicolumn{3}{c}{Random Walk Metropolis Hastings jointly drawing the entire $\theta$ vector using Garthwaite, Fan and Sisson (2015)} \\
& \multicolumn{3}{c}{to control the variance matrix of the Multivariate Gaussian proposal distribution} \\
\hline
VB  & \multicolumn{2}{c|}{Variational Bayes using (\ref{rpDeriv}) to update parameters of a} & Variational Bayes using (\ref{scoreDeriv}) to update parameters of a six \\
Standard & \multicolumn{2}{c|}{Multivariate Gaussian approximation with non-zero covariance} & component mixture of diagonal variance Multivariate Gaussians\\
\hline
VB & \multicolumn{2}{c|}{Variational Bayes using (\ref{rpUpdate}) to update parameters of a} &  Variational Bayes using (\ref{scoreUpdate}) to update parameters of a six \\
Updating & \multicolumn{2}{c|}{Multivariate Gaussian approximation with non-zero covariance} & component mixture of diagonal variance Multivariate Gaussians\\ \\
\hline
\end{tabular}}
\label{tableAlg}
\caption{Details of the algorithms used to produce posterior distributions for each method and prior combination}
\end{table}
\end{center}

@@

\section{Conclusion}

>>>>

\begin{center}
\begin{table}[h]
\resizebox{\textwidth}{!}{%
\begin{tabular}{| l | c | c | c |}
\hline
& Non-Informative Prior & Simple Hierarchy & Finite Mixture Hierarchy \\
\hline
MCMC & \multicolumn{3}{c|}{Random Walk Metropolis Hastings jointly drawing the entire $\theta$ vector using Garthwaite, Fan and Sisson (2015)} \\
& \multicolumn{3}{c|}{to control the variance matrix of the Multivariate Gaussian proposal distribution} \\
\hline
VB  & \multicolumn{2}{c|}{Variational Bayes using (\ref{rpDeriv}) to update parameters of a} & Variational Bayes using (\ref{scoreDeriv}) to update parameters of a six \\
Standard & \multicolumn{2}{c|}{Multivariate Gaussian approximation with non-zero covariance} & component mixture of diagonal variance Multivariate Gaussians\\
\hline
VB & \multicolumn{2}{c|}{Variational Bayes using (\ref{rpUpdate}) to update parameters of a} &  Variational Bayes using (\ref{scoreUpdate}) to update parameters of a six \\
Updating & \multicolumn{2}{c|}{Multivariate Gaussian approximation with non-zero covariance} & component mixture of diagonal variance Multivariate Gaussians\\ 
\hline
\end{tabular}}
\label{tableAlg}
\caption{Details of the algorithms used to produce posterior distributions for each method and prior combination}
\end{table}
\end{center}

@@

\section{Conclusion}
\begin{itemize}
\item Fitting individual AR 2 models on each driver's velocity and steering angle drastically improves forecasts of the future trajectory compared to the constant model used in practice
\item Strong prior information improves forecasts early on in the sample, but has a reduced impact after ~20 seconds of observation
\item Constantly fitting individual models in this way can be made computationally feasible by updating previous Variational Bayes model fits, which incurs only a small performance hit relative to the more expensive standard VB and MCMC methods.
\end{itemize}
